Comb associative operads

### 2018-07-19 CAs_operads.tex
Modifications

In this section, we define comb associative operads and we show that the
set of such operads admits a lattice structure, isomorphic to the lattice
division for nonnegative integers. We also relate this lattice to the
lattice of linear magmatic quotients.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comb associative operads}

Let, for any integer $\gamma \geq 1$, the binary trees
\begin{equation}
    \LComb{\gamma} :=
    \underbrace{(\dots (\Product \circ_1 \Product) \circ_1 \dots)
        \circ_1 \Product}
    _{\gamma \mbox{ \footnotesize operands}}
\end{equation}
and
\begin{equation}
    \RComb{\gamma} :=
    \underbrace{\Product \circ_2
        (\dots \circ_2 (\Product \circ_2 \Product) \dots)}
    _{\gamma \mbox{ \footnotesize operands}}
\end{equation}
be respectively the left and the right comb of degree $\gamma$.
Let us now define for any $\gamma \geq 1$ the \Def{$\gamma$-comb
associative operad} $\CAs{\gamma}$ as the quotient operad
$\Mag/_{\CongrCAs{\gamma}}$ where $\CongrCAs{\gamma}$ is the smallest
operad congruence of $\Mag$ satisfying
\begin{equation} \label{equ:congruence_CAs_gamma}
    \LComb{\gamma} \enspace \CongrCAs{\gamma} \enspace \RComb{\gamma}.
\end{equation}
Notice that $\CongrCAs{1}$ is trivial so that
$\CAs{1} = \Mag$ and that $\CongrCAs{2}$ is the operad congruence
defined by
\begin{equation}
    \begin{tikzpicture}[xscale=.24,yscale=.24,Centering]
        \node(0)at(0.00,-3.33){};
        \node(2)at(2.00,-3.33){};
        \node(4)at(4.00,-1.67){};
        \node[NodeST](1)at(1.00,-1.67)
            {\begin{math}\Product\end{math}};
        \node[NodeST](3)at(3.00,0.00)
            {\begin{math}\Product\end{math}};
        \draw[Edge](0)--(1);
        \draw[Edge](1)--(3);
        \draw[Edge](2)--(1);
        \draw[Edge](4)--(3);
        \node(r)at(3.00,1.5){};
        \draw[Edge](r)--(3);
    \end{tikzpicture}
    \Congr
    \begin{tikzpicture}[xscale=.24,yscale=.24,Centering]
        \node(0)at(0.00,-1.67){};
        \node(2)at(2.00,-3.33){};
        \node(4)at(4.00,-3.33){};
        \node[NodeST](1)at(1.00,0.00)
                {\begin{math}\Product\end{math}};
        \node[NodeST](3)at(3.00,-1.67)
                {\begin{math}\Product\end{math}};
        \draw[Edge](0)--(1);
        \draw[Edge](2)--(3);
        \draw[Edge](3)--(1);
        \draw[Edge](4)--(3);
        \node(r)at(1.00,1.5){};
        \draw[Edge](r)--(1);
    \end{tikzpicture}\,
\end{equation}
so that $\CAs{2} = \As$.
Let also
\begin{equation}
    \CAsAll := \left\{\CAs{\gamma} : \gamma\geq 1\right\}
\end{equation}
be the set of all the $\gamma$-comb associative operads.
\medbreak

@@

Recall that
$\LRank(\Tfr)$ denotes the left rank of a binary tree $\Tfr$, defined in
Section~\ref{sec:operad_Mag}.
\medbreak

\begin{Lemma}\label{lem:left_rank_and_CongrCAs}
    Let $\gamma$ be a strictly positive integer and let $\Tfr$ and
    $\Tfr'$ be two binary trees. If $\Tfr \CongrCAs{\gamma} \Tfr'$, then
    \begin{equation}
        \LRank(\Tfr) \mod \gamma - 1
        \enspace = \enspace
        \LRank(\Tfr') \mod \gamma - 1.
    \end{equation}
\end{Lemma}
\begin{proof}
  We consider the rewrite rule $\LComb{\gamma} \Rew \RComb{\gamma}$ on
  $\Mag$. 
    \smallbreak

    First, we show that $\Tfr \RewContext \Tfr'$ implies that
    $\LRank\left(\Tfr'\right) - \LRank\left(\Tfr\right)$ is
    divisible by $\gamma - 1$. \Todo{à faire.}
    \smallbreak

    Assume that $\Tfr \RewContextRT \Tfr'$, so that there exist binary trees
    $\Tfr_1$, \dots, $\Tfr_k$ such that $\Tfr_1 = \Tfr$,
    $\Tfr_k = \Tfr'$ and for every $i \in \{1, \dots, k - 1\}$, we have
    $\Tfr_i\RewContext \Tfr_{i + 1}$. The integer
    \begin{math}
        \LRank\left(\Tfr_{i + 1}\right)
        -
        \LRank\left(\Tfr_i\right)
    \end{math}
    is divisible by $\gamma - 1$ from the first part of the proof, so
    that $\LRank\left(\Tfr'\right) - \LRank\left(\Tfr\right)$ is
    divisible by $\gamma-1$.
    \smallbreak

    Assume that $\Tfr \RewContextRST \Tfr'$, so that there exist binary trees
    $\Tfr_1$, \dots, $\Tfr_k$ such that $\Tfr_1 = \Tfr$,
    $\Tfr_k = \Tfr'$ and for every $i \in \{1, \dots, k - 1\}$, we have
    $\Tfr_i \RewContextRT \Tfr_{i + 1}$ or $\Tfr_{i + 1} \RewContextRT
    \Tfr_i$. From the second part of the proof, the integer
    \begin{math}
        \LRank\left(\Tfr_{i + 1}\right)
        -
        \LRank\left(\Tfr_i\right)
    \end{math}
    is divisible by $\gamma - 1$, so that
    $\LRank\left(\Tfr'\right) - \LRank\left(\Tfr\right)$ is
    divisible by $\gamma - 1$.
    \smallbreak

    The congruence $\CongrCAs{\gamma}$ is the equivalence relation
    induced by the rewrite relation $\RewContext$ induced by the rewrite
    rule $\LComb{\gamma} \Rew \RComb{\gamma}$, that is we have $\Tfr
    \CongrCAs{\gamma} \Tfr'$ if and only if $\Tfr \RewContextRST \Tfr'$.
    Hence, from the third part of the proof, $\Tfr \CongrCAs{\gamma}
    \Tfr'$ implies that
    \begin{math}
        \LRank\left(\Tfr'\right) - \LRank\left(\Tfr\right)
    \end{math}
    is divisible by $\gamma - 1$.
\end{proof}
\medbreak

\begin{Proposition} \label{prop:division_CAs}
    Let $\gamma$ and $\gamma'$ be two positive integers. Then, there
    exists a morphism $\varphi:\CAs{\gamma'} \to \CAs{\gamma}$ if and
    only if $\left(\gamma - 1\right) \mid \left(\gamma' - 1\right)$.
\end{Proposition}
\begin{proof}
    From Lemma~\ref{lem:morphism_CAs}, it is enough to show that
    $\LComb{\gamma'} \CongrCAs{\gamma} \RComb{\gamma'}$ if and only if
    $\left(\gamma-1\right) \mid \left(\gamma'-1\right)$. If
    $\LComb{\gamma'}\CongrCAs{\gamma}\RComb{\gamma'}$, from
    Lemma~\ref{lem:left_rank_and_CongrCAs},
    \begin{math}
        \LRank\left(\LComb{\gamma'}\right)
        - \LRank\left(\RComb{\gamma'}\right)
        = \gamma' - 1
    \end{math}
    is divisible by $\gamma-1$, which shows the direct implication.
    \smallbreak

@@

    $\left(\gamma-1\right) \mid \left(\gamma'-1\right)$, the rewrite

@@

            \draw[Edge,dotted](1)--(3);

@@

            \draw[Edge,dotted](5)--(7);

@@

            \draw[Edge,dotted](9)--(11);

@@

            \node[fit=(1)(3),rotate fit=0,inner sep=0pt,
                rounded corners,draw=Col5!80]{};
            \node[fit=(5)(7),rotate fit=0,inner sep=0pt,
                rounded corners,draw=Col5!80]{};
            \node[fit=(9)(11),rotate fit=0,inner sep=0pt,
                rounded corners,draw=Col5!80]{};

@@

        \enspace \Rew \enspace

@@

            \draw[Edge,dotted](13)--(11);

@@

            \node[fit=(1)(3),rotate fit=0,inner sep=0pt,
                rounded corners,draw=Col5!80]{};
            \node[fit=(5)(7),rotate fit=0,inner sep=0pt,
                rounded corners,draw=Col5!80]{};
            \node[fit=(11)(13),rotate fit=0,inner sep=0pt,
                rounded corners,draw=Col5!80]{};
        \enspace \Rew \enspace

@@

            \draw[Edge,dotted](9)--(7);

@@

            \node[fit=(1)(3),rotate fit=0,inner sep=0pt,
                rounded corners,draw=Col5!80]{};
            \node[fit=(7)(9),rotate fit=0,inner sep=0pt,
                rounded corners,draw=Col5!80]{};
            \node[fit=(11)(13),rotate fit=0,inner sep=0pt,
                rounded corners,draw=Col5!80]{};
        \enspace \RewRT \enspace

@@

            \draw[Edge,dotted](5)--(3);

@@

            \node[fit=(3)(5),rotate fit=0,inner sep=0pt,
                rounded corners,draw=Col5!80]{};
            \node[fit=(7)(9),rotate fit=0,inner sep=0pt,
                rounded corners,draw=Col5!80]{};
            \node[fit=(11)(13),rotate fit=0,inner sep=0pt,
                rounded corners,draw=Col5!80]{};

@@

\begin{Theorem}\label{thm:lattice_CAs}
  The tuple $\LatCAs$ is a lattice, where $\InfCAs$ and $\SupCAs$ are
  defined, for any positive integers $\gamma$ and $\gamma'$, as follows:
    \begin{equation}
      \CAs{\gamma}\InfCAs\CAs{\gamma'}=\CAs{\gcd \left(\gamma-1, \gamma'-1\right)}
    \end{equation}
    and
    \begin{equation}
      \CAs{\gamma}\SupCAs\CAs{\gamma'}=\CAs{\lcm \left(\gamma-1, \gamma'-1\right)}.
    \end{equation}
\end{Theorem}
\medbreak

@@

\begin{Theorem}
  The inclusion
  $\iota:\left(\KCAsAll,\OrdCAs\right)\to\left(\QMag,\OrdQMag\right)$ is
  non decreasing. In particular, for any positive integers $\gamma$ and
  $\gamma'$, we have
  \begin{equation} \label{equ:comparison_of_lattice_operations}
    \KCAs{\gcd \left(\gamma-1, \gamma'-1\right)}\OrdQMag
    \KCAs{\gamma}\InfQMag\KCAs{\gamma'}
  \end{equation}
  and
  \begin{equation}
    \KCAs{\gamma}\SupQMag\KCAs{\gamma'}\OrdQMag
    \KCAs{\lcm \left(\gamma-1, \gamma'-1\right)}.
  \end{equation}

  \end{Theorem}

@@

From Proposition~\ref{prop:PBW_basis_CAs_3}, and by using a result
of~\cite{Gir18} describing a system of equations for the generating
series of syntax trees avoiding some sets of subtrees, we obtain the
following result.
\medbreak

>>>>

In this section, we define comb associative operads and we show that the
set of such operads admits a lattice structure, isomorphic to the lattice
division for nonnegative integers. We also relate this lattice to the
lattice of linear magmatic quotients.
\medbreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comb associative operads}
Recall first that the \Def{associative operad} $\As$ is the quotient
of $\Mag$ by the smallest operad congruence $\Congr$ satisfying
\begin{equation}
    \begin{tikzpicture}[xscale=.24,yscale=.24,Centering]
        \node(0)at(0.00,-3.33){};
        \node(2)at(2.00,-3.33){};
        \node(4)at(4.00,-1.67){};
        \node[NodeST](1)at(1.00,-1.67)
            {\begin{math}\Product\end{math}};
        \node[NodeST](3)at(3.00,0.00)
            {\begin{math}\Product\end{math}};
        \draw[Edge](0)--(1);
        \draw[Edge](1)--(3);
        \draw[Edge](2)--(1);
        \draw[Edge](4)--(3);
        \node(r)at(3.00,1.5){};
        \draw[Edge](r)--(3);
    \end{tikzpicture}
    \Congr
    \begin{tikzpicture}[xscale=.24,yscale=.24,Centering]
        \node(0)at(0.00,-1.67){};
        \node(2)at(2.00,-3.33){};
        \node(4)at(4.00,-3.33){};
        \node[NodeST](1)at(1.00,0.00)
                {\begin{math}\Product\end{math}};
        \node[NodeST](3)at(3.00,-1.67)
                {\begin{math}\Product\end{math}};
        \draw[Edge](0)--(1);
        \draw[Edge](2)--(3);
        \draw[Edge](3)--(1);
        \draw[Edge](4)--(3);
        \node(r)at(1.00,1.5){};
        \draw[Edge](r)--(1);
    \end{tikzpicture}\,.
\end{equation}
We propose here a generalization of $\Congr$ in order to define
generalizations of $\As$.
\medbreak

Let, for any integer $\gamma \geq 1$, the binary trees $\LComb{\gamma}$
and $\RComb{\gamma}$ be respectively the left and the right comb of
degree $\gamma$. These trees are depicted as
\begin{equation}
    \LComb{\gamma} = \enspace
    \begin{tikzpicture}[xscale=.26,yscale=.3,Centering]
        \node(0)at(0.00,-5.25){};
        \node(2)at(2.00,-5.25){};
        \node(4)at(4.00,-3.50){};
        \node(6)at(6.00,-1.75){};
        \node[NodeST](1)at(1.00,-3.50){\begin{math}\Product\end{math}};
        \node[NodeST](3)at(3.00,-1.75){\begin{math}\Product\end{math}};
        \node[NodeST](5)at(5.00,0.00){\begin{math}\Product\end{math}};
        \draw[Edge](0)--(1);
        \draw[Edge,dotted](1)edge[]node[font=\tiny]{
            \begin{math}\gamma\! -\! 1\end{math}\hspace*{.6cm}}(3);
        \draw[Edge](2)--(1);
        \draw[Edge](3)--(5);
        \draw[Edge](4)--(3);
        \draw[Edge](6)--(5);
        \node(r)at(5.00,1.5){};
        \draw[Edge](r)--(5);
    \end{tikzpicture}
    \qquad \mbox{and} \qquad
    \RComb{\gamma} =
    \begin{tikzpicture}[xscale=.26,yscale=.3,Centering]
        \node(0)at(0.00,-1.75){};
        \node(2)at(2.00,-3.50){};
        \node(4)at(4.00,-5.25){};
        \node(6)at(6.00,-5.25){};
        \node[NodeST](1)at(1.00,0.00){\begin{math}\Product\end{math}};
        \node[NodeST](3)at(3.00,-1.75){\begin{math}\Product\end{math}};
        \node[NodeST](5)at(5.00,-3.50){\begin{math}\Product\end{math}};
        \draw[Edge](0)--(1);
        \draw[Edge](2)--(3);
        \draw[Edge](3)--(1);
        \draw[Edge](4)--(5);
        \draw[Edge,dotted](5)edge[]node[font=\tiny]{
            \hspace*{.6cm}\begin{math}\gamma\! -\! 1\end{math}}(3);
        \draw[Edge](6)--(5);
        \node(r)at(1.00,1.5){};
        \draw[Edge](r)--(1);
    \end{tikzpicture}\,,
\end{equation}
where the values on the dotted edges denote the number of internal
nodes they contain. We shall employ this drawing convention in the
sequel, combined with the convention stipulating that dotted edges
with no value have any number of internal nodes. Let us now define for
any $\gamma \geq 1$ the \Def{$\gamma$-comb associative operad}
$\CAs{\gamma}$ as the quotient operad $\Mag/_{\CongrCAs{\gamma}}$ where
$\CongrCAs{\gamma}$ is the smallest operad congruence of $\Mag$
satisfying
\begin{equation} \label{equ:congruence_CAs_gamma}
    \LComb{\gamma} \enspace \CongrCAs{\gamma} \enspace \RComb{\gamma}.
\end{equation}
Notice that $\CongrCAs{1}$ is trivial so that
$\CAs{1} = \Mag$ and that $\CongrCAs{2}$ is the operad congruence
defining $\As$ so that $\CAs{2} = \As$. Let also
\begin{equation}
    \CAsAll := \left\{\CAs{\gamma} : \gamma\geq 1\right\}
\end{equation}
be the set of all the $\gamma$-comb associative operads.
\medbreak

@@

Recall that
$\LRank(\Tfr)$ denotes the left rank of a binary tree $\Tfr$, defined in
Section~\ref{sec:operad_Mag}. Besides, to simplify the notation,
we shall write $\bar{a}$ instead of $a - 1$ for any integer $a$.
\medbreak

\begin{Lemma}\label{lem:left_rank_and_CongrCAs}
    Let $\gamma$ be a positive integer and let $\Tfr$ and
    $\Tfr'$ be two binary trees. If $\Tfr \CongrCAs{\gamma} \Tfr'$, then
    \begin{equation}
        \LRank(\Tfr) \pmod{\bar{\gamma}}
        \enspace = \enspace
        \LRank\left(\Tfr'\right) \pmod{\bar{\gamma}}.
    \end{equation}
\end{Lemma}
\begin{proof}
  We consider the rewrite rule $\LComb{\gamma} \Rew \RComb{\gamma}$ on
  $\Mag$.
    \smallbreak

    First, we show that $\Tfr \RewContext \Tfr'$ implies that
    $\LRank\left(\Tfr'\right) - \LRank\left(\Tfr\right)$ is
    divisible by $\bar{\gamma}$. \Todo{à faire.}
    \smallbreak

    Assume that $\Tfr \RewContextRT \Tfr'$, so that there exist binary trees
    $\Tfr_1$, \dots, $\Tfr_k$ such that $\Tfr_1 = \Tfr$,
    $\Tfr_k = \Tfr'$ and for every $i \in [k - 1]$, we have
    $\Tfr_i\RewContext \Tfr_{i + 1}$. The integer
    \begin{math}
        \LRank\left(\Tfr_{i + 1}\right)
        -
        \LRank\left(\Tfr_i\right)
    \end{math}
    is divisible by $\bar{\gamma}$ from the first part of the proof, so
    that $\LRank\left(\Tfr'\right) - \LRank\left(\Tfr\right)$ is
    divisible by~$\bar{\gamma}$.
    \smallbreak

    Assume that $\Tfr \RewContextRST \Tfr'$, so that there exist binary trees
    $\Tfr_1$, \dots, $\Tfr_k$ such that $\Tfr_1 = \Tfr$,
    $\Tfr_k = \Tfr'$ and for every $i \in [k - 1]$, we have
    $\Tfr_i \RewContextRT \Tfr_{i + 1}$ or $\Tfr_{i + 1} \RewContextRT
    \Tfr_i$. From the second part of the proof, the integer
    \begin{math}
        \LRank\left(\Tfr_{i + 1}\right)
        -
        \LRank\left(\Tfr_i\right)
    \end{math}
    is divisible by $\bar{\gamma}$, so that
    $\LRank\left(\Tfr'\right) - \LRank\left(\Tfr\right)$ is
    divisible by~$\bar{\gamma}$.
    \smallbreak

    The congruence $\CongrCAs{\gamma}$ is the equivalence relation
    induced by the rewrite relation $\RewContext$ induced by the rewrite
    rule $\LComb{\gamma} \Rew \RComb{\gamma}$, that is we have $\Tfr
    \CongrCAs{\gamma} \Tfr'$ if and only if $\Tfr \RewContextRST \Tfr'$.
    Hence, from the third part of the proof, $\Tfr \CongrCAs{\gamma}
    \Tfr'$ implies that
    \begin{math}
        \LRank\left(\Tfr'\right) - \LRank\left(\Tfr\right)
    \end{math}
    is divisible by~$\bar{\gamma}$.
\end{proof}
\medbreak

\begin{Proposition} \label{prop:division_CAs}
    Let $\gamma$ and $\gamma'$ be two positive integers. Then, there
    exists a morphism $\varphi:\CAs{\gamma'} \to \CAs{\gamma}$ if and
    only if $\bar{\gamma} \mid \bar{\gamma'}$.
\end{Proposition}
\begin{proof}
    From Lemma~\ref{lem:morphism_CAs}, it is enough to show that
    $\LComb{\gamma'} \CongrCAs{\gamma} \RComb{\gamma'}$ if and only if
    $\bar{\gamma} \mid \bar{\gamma'}$. If
    $\LComb{\gamma'}\CongrCAs{\gamma}\RComb{\gamma'}$, from
    Lemma~\ref{lem:left_rank_and_CongrCAs},
    \begin{math}
        \LRank\left(\LComb{\gamma'}\right)
        - \LRank\left(\RComb{\gamma'}\right)
        = \bar{\gamma'}
    \end{math}
    is divisible by $\bar{\gamma}$, which shows the direct implication.
    \smallbreak

@@

    $\bar{\gamma} \mid \bar{\gamma'}$, the rewrite

@@

            \draw[Edge,dotted](1)edge[]node[font=\footnotesize]{
                \begin{math}\bar{\gamma}\end{math}\hspace*{.5cm}}(3);

@@

            \draw[Edge,dotted](5)edge[]node[font=\footnotesize]{
                \begin{math}\bar{\gamma}\end{math}\hspace*{.5cm}}(7);

@@

            \draw[Edge,dotted](9)edge[]node[font=\footnotesize]{
                \begin{math}\bar{\gamma}\end{math}\hspace*{.5cm}}(11);

@@

            %\node[fit=(1)(3),rotate fit=0,inner sep=0pt,
                %rounded corners,draw=Col5!80]{};
            %\node[fit=(5)(7),rotate fit=0,inner sep=0pt,
                %rounded corners,draw=Col5!80]{};
            %\node[fit=(9)(11),rotate fit=0,inner sep=0pt,
                %rounded corners,draw=Col5!80]{};

@@

        \enspace \RewContext \enspace

@@

            \draw[Edge,dotted](13)edge[]node[font=\footnotesize]{
                \hspace*{.5cm}\begin{math}\bar{\gamma}\end{math}}(11);

@@

            %\node[fit=(1)(3),rotate fit=0,inner sep=0pt,
                %rounded corners,draw=Col5!80]{};
            %\node[fit=(5)(7),rotate fit=0,inner sep=0pt,
                %rounded corners,draw=Col5!80]{};
            %\node[fit=(11)(13),rotate fit=0,inner sep=0pt,
                %rounded corners,draw=Col5!80]{};
        \enspace \RewContext \enspace

@@

            \draw[Edge,dotted](9)edge[]node[font=\footnotesize]{
                \hspace*{.5cm}\begin{math}\bar{\gamma}\end{math}}(7);

@@

            %\node[fit=(1)(3),rotate fit=0,inner sep=0pt,
                %rounded corners,draw=Col5!80]{};
            %\node[fit=(7)(9),rotate fit=0,inner sep=0pt,
                %rounded corners,draw=Col5!80]{};
            %\node[fit=(11)(13),rotate fit=0,inner sep=0pt,
                %rounded corners,draw=Col5!80]{};
        \enspace \RewContextRT \enspace

@@

            \draw[Edge,dotted](5)edge[]node[font=\footnotesize]{
                \hspace*{.5cm}\begin{math}\bar{\gamma}\end{math}}(3);

@@

            %\node[fit=(3)(5),rotate fit=0,inner sep=0pt,
                %rounded corners,draw=Col5!80]{};
            %\node[fit=(7)(9),rotate fit=0,inner sep=0pt,
                %rounded corners,draw=Col5!80]{};
            %\node[fit=(11)(13),rotate fit=0,inner sep=0pt,
                %rounded corners,draw=Col5!80]{};

@@

\begin{Theorem}\label{thm:lattice_CAs}
  The tuple $\LatCAs$ is a lattice, where $\InfCAs$ and $\SupCAs$ are
  defined, for any positive integers $\gamma$ and $\gamma'$, by
    \begin{equation}
      \CAs{\gamma}\InfCAs\CAs{\gamma'}
      =\CAs{\gcd \left(\bar{\gamma}, \bar{\gamma'}\right)}
    \end{equation}
    and
    \begin{equation}
      \CAs{\gamma}\SupCAs\CAs{\gamma'}
      =\CAs{\lcm \left(\bar{\gamma}, \bar{\gamma'}\right)}.
    \end{equation}
\end{Theorem}
\medbreak

@@

\begin{Theorem}
    The inclusion
    \begin{math}
        \iota:\left(\KCAsAll,\OrdCAs\right)
        \to
        \left(\QMag,\OrdQMag\right)
    \end{math}
    is nondecreasing. In particular, for any positive integers $\gamma$
    and $\gamma'$, we have
    \begin{equation} \label{equ:comparison_of_lattice_operations}
        \KCAs{\gcd \left(\bar{\gamma}, \bar{\gamma'}\right)}
        \OrdQMag
        \KCAs{\gamma}\InfQMag\KCAs{\gamma'}
    \end{equation}
    and
    \begin{equation}
        \KCAs{\gamma}\SupQMag\KCAs{\gamma'}
        \OrdQMag
        \KCAs{\lcm \left(\bar{\gamma}, \bar{\gamma'}\right)}.
    \end{equation}
\end{Theorem}

@@

From Proposition~\ref{prop:PBW_basis_CAs_3}, and by using a result
of~\cite{Gir18} (see also~\cite{Row10,KP15}) describing a system of
equations for the generating series of syntax trees avoiding some sets
of subtrees, we obtain the following result.
\medbreak
